Main Analysis

### 2024-05-13 Manuscript Analysis/main_analysis.Rmd
perceived listening effort ratings

@@

>>>>

phrase_acc_df <- phrase_acc |>
  dplyr::select(subject, trial, target_number, correct_words_initial, rep_acc)

@@

The speaker characteristics are listed below. Note: 41 trials were removed because they had missing listener responses (i.e. audio file cut out, etc.). Therefore, the summary statistics are based on 2679 trials total.

ple_data <- rio::import("Cleaned Data/cleaned_ple_data.csv") |>
  dplyr::left_join(phrase_acc_df, by = c("subject", "trial")) |>
  dplyr::mutate(speaker = factor(speaker, levels = c("Control", "ALS")),
                trial_c = trial - 6,
                rep_acc = factor(rep_acc, levels = c("accurate", "inaccurate")))

speaker_table <- ple_data |>
  dplyr::filter(!is.na(rep_acc)) |>
  dplyr::select(subject, trial, speaker, correct_words_initial, target_number, rep_acc) |>
  dplyr::mutate(intel = (correct_words_initial/target_number)*100) |>
  dplyr::select(-c(subject, trial, correct_words_initial, target_number)) |>
  tbl_summary(by = speaker,
              type = list(intel ~ "continuous",
                          rep_acc ~ "categorical"),
              statistic = list(all_continuous() ~ "{mean} ({sd})",
                               all_categorical() ~ "{n} ({p}%)"),
              digits = list(everything() ~ c(2)),
              label = list(intel ~ "Intelligibility",
                           rep_acc ~ "Repetition Accuracy")) |>
  as_gt()

speaker_table

speaker_table |>
  gt::gtsave("Tables/speaker_table.html")

# Perceived Listening Effort Ratings

## Descriptives

ple_data |>
  dplyr::select(speaker, effort_rating, rep_acc) |>
  dplyr::filter(!is.na(rep_acc)) |>
  tbl_strata(
    strata = rep_acc,
    ~.x |>
      tbl_summary(
        by = speaker,
        type = list(effort_rating ~ "continuous"),
        statistic = list(all_continuous() ~ c("{mean} ({sd})")),
        missing = "no",
        digits = all_continuous() ~ 2,
        label = list(effort_rating ~ "Perceived Listening Effort")
      ))

## PLE Models

Linear mixed effects (LME) models were used to test the influence of speaker (Control vs ALS) and phrase repetition accuracy (accurate vs inaccurate) on perceived listening effort ratings. We used a model-building approach for this analysis. The steps are detailed below.

### Fully Unconditional Model

ple_data <- ple_data |>
  dplyr::filter(!is.na(rep_acc))

m0_ple <- glmmTMB(effort_rating ~ 1 + (1|subject) + (1|code), data = ple_data)
sjPlot::tab_model(m0_ple, pred.labels = "Intercept",
                  dv.labels = "Perceived Listening Effort")

performance::icc(m0_ple)

```
### PLE Model 1

In this step, we are adding trial order (trial_c) as a random slop for both the listener (subject) and phrase (code) random intercepts. The random intercept of trial order significantly improved model fit.

m1_ple <- glmmTMB(effort_rating ~ 1 + (trial_c|subject) + (trial_c|code), data = ple_data)
sjPlot::tab_model(m1_ple, pred.labels = "Intercept",
                  dv.labels = "Perceived Listening Effort")

performance::test_performance(m0_ple, m1_ple)

```
### PLE Model 2

Trial order is the first random effect added to the model. Trial order is added in order to control for any possible order effects in the data. As noted in the results below, adding trial order did not significantly improve model fit to the data. However, I'll leave this fixed effect in the model to act as a covariate.

m2_ple <- glmmTMB(effort_rating ~ trial_c + (trial_c|subject) + (trial_c|code), data = ple_data)
sjPlot::tab_model(m2_ple, 
                  pred.labels = c("Intercept", "Trial Order"),
                  dv.labels = "Perceived Listening Effort")

performance::test_performance(m1_ple, m2_ple)

### PLE Model 3

Adding the main fixed effect of speaker significantly improved the model fit.

m3_ple <- glmmTMB(effort_rating ~ trial_c + speaker + (trial_c|subject) + (trial_c|code), data = ple_data)
sjPlot::tab_model(m3_ple,
                  pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]"),
                  dv.labels = "Perceived Listening Effort")

performance::test_performance(m2_ple, m3_ple)

### PLE Model 4

The main fixed effect of repetition accuracy significantly improved model fit.

m4_ple <- glmmTMB(effort_rating ~ trial_c + speaker + rep_acc + (trial_c|subject) + (trial_c|code), data = ple_data)
sjPlot::tab_model(m4_ple,
                  pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]"),
                  dv.labels = "Perceived Listening Effort")

performance::test_performance(m3_ple, m4_ple)

```
### PLE Model 5

The interaction term between speaker and repetition accuracy did not significantly improve model fit. This indicates that the magnitude between accurate and inaccurate ratings was similar for both speakers.

m5_ple <- glmmTMB(effort_rating ~ trial_c + speaker + rep_acc + speaker*rep_acc + (trial_c|subject) + (trial_c|code), data = ple_data)
sjPlot::tab_model(m5_ple,
                  pred.labels = c("Intercept", "Trial Order", "Speaker [ALS]", "Repetition Accuracy [Inaccurate]",
                                  "Speaker [ALS] * Repetition Accuracy [Inaccurate]"),
                  dv.labels = "Perceived Listening Effort")

performance::test_performance(m4_ple, m5_ple)

## Plot

model_ple <- m5_ple |>
  sjPlot::plot_model(type = "int")

plot_data_ple <- model_ple[["data"]] |>
  as.data.frame()
